Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-24 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Changed image

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{Sample of users, showing the {\tt knows} relationship.}
    \label{fig:users-graph}
\end{figure}

@@

Using a graph database provided certain advantages when monitoring the experiments, for instance 
using the query language

>>>>

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/users_known_1.png}
    \caption{Comparasion of two users showing the {\tt knows} relationship.}
    \label{fig:users-graph}
\end{figure}

@@

Using the Noe4J graph database and the Cypher query language when monitoring the experiments provided 
views on the connected data difficult to replicate in a relational database. An example view is presented 
in figure \ref{fig:users-graph} showing comparasion between two users on the degree of the 
{\tt has} relationship.
